---
title: "Singing in the rain! Climate constraints on the occurrence of indri’s song"
author: "Valeria Ferrario"
date: "2024-04-30"
output:
  word_document: default
  html_document: default
  pdf_document: default
---

```{r}
pacman::p_load(ggpubr,ggplot2, dplyr, tidyr, tidyverse,geosphere, sjPlot,gridExtra, 
               lubridate,bbmle,stringr,ggsci,suncalc, lunar, lme4,plyr,bbmle,stringr,
               MuMIn, car, sp, gstat, cowplot, coefplot, ggrepel)
```

Read dataset with the detections from the automated detection algorithm and the one with the detections of the weather station
```{r}

indri.dat <- read.csv("/Volumes/V/SCRIPT/Indri_rain/indri_detections.csv")

meteo_united <- read.csv("/Volumes/V/SCRIPT/Indri_rain/meteo/Meteo_united_vr3.csv")
meteo_united <- meteo_united %>% mutate(datetime = as.POSIXct(datetime, format="%d/%m/%Y %H:%M", tz="UTC")) %>% arrange(datetime) %>% na.omit() %>% mutate(date = format(datetime, "%Y-%m-%d"))
```

Extract 'period' as the time span going from 6 a.m. for the next 24 hours, 
if you don't have this variable already in the dataset
```{r}

meteo_united <- meteo_united %>% mutate(datetime = as.POSIXct(datetime), period = as.integer(difftime(datetime, floor_date(min(datetime), "day") + hours(6), units = "hours") / 24) + 1)

```

Read dataset with coordinates 

```{r}

coordinates <- read.csv("/Volumes/V/SCRIPT/Indri_rain/coordinates_rain.csv") %>% select(-X) %>% distinct()
```

PART 1: Influence of environmental variables on indri song events

Convert 'date' and 'hours' columns to character and create 'date_h' column
```{r}

indri_part1 <- indri.dat
indri_part1$date <- as.character(indri_part1$date)
indri_part1$date_h <- paste0(indri_part1$hours, "_", indri_part1$date)

meteo_part1 <- meteo_united
meteo_part1$hours <- as.POSIXlt(meteo_part1$datetime)$hour
meteo_part1$date <- as.character(meteo_part1$date)
meteo_part1$date_h <- paste0(meteo_part1$hours, "_", meteo_part1$date)

# Merge datasets by 'date_h'
events <- merge(indri_part1, meteo_part1, by="date_h" )

# Remove unnecessary columns from 'events'
events <- events %>% select(-datetime.y, -date.y, -hours.y )

# Aggregate data and calculate mean for specific columns
columns_to_mean <- events[, c("song")]

events1 <- aggregate(columns_to_mean,by = list(period = events$period,place = events$place,rain = events$rain_sum, temp_night = events$night_temp_mean, temp_day = events$day_temp_mean, night_rain = events$night_rain_sum, recorder = events$recorder, temp = events$temp_mean, date = events$date.x), FUN = mean)

# Convert 'x' column to binary 'bin.detections' column
events1$bin.detections <- as.integer(ifelse(events1$x== 0, 0, 1))

# Scale numeric variables
events1$rain_scaled <- scale(events1$rain)
events1$temp_scaled <- scale(events1$temp)
events1$night_rain_scaled <- scale(events1$night_rain)

# Convert 'date' to Date class and create 'year' column
events1$date <- as.Date(events1$date)
events1$year <-  as.factor(format(events1$date, "%Y"))


# Models
song.aggregate.intercept <- glmer(bin.detections ~ (1|recorder) + (1|period), data=events1, family = "binomial")

song.aggregate.night <- glmer(bin.detections ~ night_rain_scaled + year + (1|recorder) + (1|period), data=events1, family = "binomial")

song.aggregate.rain <- glmer(bin.detections ~ rain_scaled + year + (1|recorder) + (1|period), data=events1, family = "binomial")

song.aggregate.temp <- glmer(bin.detections ~ temp_scaled + year + (1|recorder) + (1|period), data=events1, family = "binomial")

song.aggregate.night.rain <- glmer(bin.detections ~ night_rain_scaled + rain_scaled + year + (1|recorder) + (1|period), data=events1, family = "binomial")

song.aggregate.night.temp <- glmer(bin.detections ~ night_rain_scaled + temp_scaled + year + (1|recorder) + (1|period), data=events1, family = "binomial")

song.aggregate.rain.temp <- glmer(bin.detections ~ rain_scaled + temp_scaled + year + (1|recorder) + (1|period), data=events1, family = "binomial")

song.aggregate.night.rain.temp <- glmer(bin.detections ~ night_rain_scaled + rain_scaled + temp_scaled + year + (1|recorder) + (1|period) ,data=events1, family = "binomial")

song.aggregate.night_rain <- glmer(bin.detections ~ night_rain_scaled * rain_scaled + year + (1|recorder) + (1|period), data=events1, family = "binomial")

song.aggregate.night_temp <- glmer(bin.detections ~ night_rain_scaled * temp_scaled + year + (1|recorder) + (1|period), data=events1, family = "binomial")

song.aggregate.rain_temp <- glmer(bin.detections ~ rain_scaled * temp_scaled + year + (1|recorder) + (1|period), data=events1, family = "binomial")

song.aggregate.night_rain_temp <- glmer(bin.detections ~ night_rain_scaled * rain_scaled * temp_scaled + year + (1|recorder) + (1|period),data = events1, family = "binomial",   control = glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 2e5)))

song.aggregate.night.rain_temp <- glmer(bin.detections ~ night_rain_scaled + rain_scaled * temp_scaled + year + (1|recorder) + (1|period), data=events1, family = "binomial")

# AIC Comparison
AICtab(song.aggregate.intercept, song.aggregate.night, song.aggregate.rain, song.aggregate.temp,song.aggregate.night.rain, song.aggregate.night.temp, song.aggregate.rain.temp, song.aggregate.night.rain.temp, song.aggregate.night_rain, song.aggregate.night_temp, song.aggregate.rain_temp, song.aggregate.night_rain_temp, song.aggregate.night.rain_temp, weights=T, base=T)

```

```{r}
# Model Summaries
summary(song.aggregate.night.rain.temp)
summary(song.aggregate.rain_temp)
summary(song.aggregate.night.rain_temp)
summary(song.aggregate.rain.temp)

```

```{r}
# VIF Check
VIF <- events1
VIF$bin.detections <- as.numeric(VIF$bin.detections)
predictor_vars <- c("temp", "rain", "night_rain")
lm_model <- lm(bin.detections ~ ., data = VIF[, c("bin.detections", predictor_vars)])
car::vif(lm_model)
```




PART 2: Influence of environmental variables on indri-singing events (count)
```{r}

count_ds <- events %>% select(datetime.x, song) %>% group_by(datetime = datetime.x) %>% dplyr::summarize(song_count = sum(song)) %>% mutate(song = ifelse(song_count > 1, 1, 0))

count_ds$datetime <- as.POSIXct(count_ds$datetime, format="%Y-%m-%d %H:%M:%S", tz = "UTC")

c_meteo_ds <- merge(count_ds, meteo_united, by = c("datetime"))

c_meteo_ds$year <- format(c_meteo_ds$datetime, "%Y")

c_meteo_ds <- c_meteo_ds %>% group_by(period,year, max_temp, min_temp, rain =rain_sum, night_rain =night_rain_sum, night_temp = night_temp_mean,day_temp=day_temp_mean) %>% dplyr::summarise( songs = sum(song), temp = mean(temp)) %>% na.omit()

# Scaling variables
c_meteo_ds$rain_scaled <- scale(c_meteo_ds$rain)
c_meteo_ds$temp_scaled <- scale(c_meteo_ds$temp)
c_meteo_ds$night_rain_scaled <- scale(c_meteo_ds$night_rain)

# Models 
mod.intercept <- glmer(songs ~ (1|period), data=c_meteo_ds,family=poisson)

mod.night <- glmer(songs ~ night_rain_scaled + year + (1|period), data=c_meteo_ds, family=poisson)

mod.rain <- glmer(songs ~ rain_scaled + year + (1|period), data=c_meteo_ds, family=poisson)

mod.temp <- glmer(songs ~ temp_scaled + year + (1|period), data=c_meteo_ds, family=poisson)

mod.rain.night <- glmer(songs ~ rain_scaled + night_rain_scaled + year + (1|period), data=c_meteo_ds, family=poisson)

mod.night.temp <- glmer(songs ~ night_rain_scaled + temp_scaled + year + (1|period), data=c_meteo_ds, family=poisson)

mod.rain.temp <- glmer(songs ~ rain_scaled + temp_scaled + year + (1|period), data=c_meteo_ds, family=poisson)

mod.night.rain.temp <- glmer(songs ~ temp_scaled + night_rain_scaled + rain_scaled + year + (1|period), data=c_meteo_ds, family=poisson)

mod.rain_night <- glmer(songs ~ rain_scaled * night_rain_scaled + year + (1|period), data=c_meteo_ds, family=poisson)

mod.night_temp <- glmer(songs ~ night_rain_scaled * temp_scaled + year + (1|period), data=c_meteo_ds, family=poisson)

mod.rain_temp <- glmer(songs ~ rain_scaled * temp_scaled  + year + (1|period), data=c_meteo_ds, family=poisson)

mod.night_rain_temp <- glmer(songs ~ night_rain_scaled * rain_scaled * temp_scaled + year + (1|period), data=c_meteo_ds, family=poisson, control = glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 2e5))) 

mod.temp_night.rain <- glmer(songs ~ temp_scaled * night_rain_scaled + rain_scaled + year + (1|period), data=c_meteo_ds, family=poisson)

mod.temp_rain.night <- glmer(songs ~ temp_scaled * rain_scaled + night_rain_scaled + year + (1|period), data=c_meteo_ds, family=poisson)

mod.rain_night.temp <- glmer(songs ~ temp_scaled + night_rain_scaled * rain_scaled + year + (1|period), data=c_meteo_ds, family=poisson, control = glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 2e5)))

mod.night.rain_temp <- glmer(songs ~ night_rain_scaled + rain_scaled * temp_scaled + year + (1|period), data=c_meteo_ds, family=poisson)

mod.night_temp.rain <- glmer(songs ~ night_rain_scaled * temp_scaled + rain_scaled  + year + (1|period), data=c_meteo_ds, family=poisson)

# AIC comparison
AICtab(mod.intercept, mod.night, mod.rain, mod.temp, mod.rain.night, mod.night.temp, mod.rain.temp,mod.night.rain.temp, mod.night.rain_temp, mod.night_temp.rain, mod.rain_night, mod.night_temp, mod.rain_temp, mod.night_rain_temp, base= T, weights=T)

# Summarise model
summary(mod.night_temp.rain)

# Check VIF 
VIF <- c_meteo_ds
VIF$song_count <- as.numeric(VIF$songs)
predictor_vars <- c(  "temp_scaled", "rain_scaled", "night_rain")
lm_model <- lm(songs ~ ., data = VIF[, c("songs", predictor_vars)])
car::vif(lm_model)
```



PART 3: Influence of environmental variables on song timing

```{R}
# -------------------------------

# Merge timing_half and coordinates by "recorder"
timing <- merge(events, coordinates, by = "recorder")

# Select specific columns
timing <- timing %>% select(recorder, date =date.x, file, datetime = datetime.x, period, rain, song, place=place.x,  time, meteostation, temp, temp_mean, rain_sum, max_temp, min_temp, night_rain_sum, night_temp_mean, day_temp_mean, ALT , N , E)

# Process the date column
timing$datetime <- as.POSIXct(timing$datetime, format = "%Y-%m-%d %H:%M:%S", tz = "UTC")

timing$date <- as.Date(timing$datetime)
timing$time <- format(timing$datetime, "%H:%M:%S")

# Remove duplicated rows
timing <- timing[!duplicated(timing), ]

# Calculate nautical dawn
nautical_dawn <- c()

for (i in 1:nrow(timing)) {nautical_dawn <- c(nautical_dawn, suncalc::getSunlightTimes(date = timing$date[i],lat = timing$N[i],lon = timing$E[i])$nauticalDawn)}


# Add nautical dawn to timing data frame
timing$nautical_dawn <- nautical_dawn
timestamp <- timing$nautical_dawn

# Convert nautical dawn to POSIXct
timing$dawn_time <- as.POSIXct(timestamp, origin = "1970-01-01", tz="UTC")

# Add 3 hours to dawn_time
timing$dawn_time <- timing$dawn_time + hours(3)
timing$minutes.til.dawn <- as.numeric(difftime(timing$datetime, timing$dawn_time, units = "mins"))

# Determine lunar phase
timing$lunar_phase <- lunar.phase(timing$date)
timing$lunar_phase <- cut(timing$lunar_phase, breaks = c(-Inf, 1.570796, 3.141593, 4.712389, Inf), labels = c("New", "Waxing", "Full", "Waning"))

# Select relevant columns and filter out rows with song = "0"
timing <- timing %>% select(minutes.til.dawn, period, song, recorder, meteostation, datetime, min_temp, night_rain =night_rain_sum, rain = rain_sum, temp = temp_mean, temp_night=night_temp_mean, 
lunar_phase, temp_day=day_temp_mean) %>% filter(song != "0")

# Convert factors
timing$recorder <- as.factor(timing$recorder)
timing$lunar_phase <- as.factor(timing$lunar_phase)

# Scale variables
timing$rain_scaled <- scale(timing$rain)
timing$temp_scaled <- scale(timing$temp)
timing$night_rain_scaled <- scale(timing$night_rain)
timing$minutes.til.dawn.sc <- scale(timing$minutes.til.dawn)

# Models
song.timing.intercept <- lmer(minutes.til.dawn.sc ~ (1|recorder) + (1|period), data = timing, REML = F)

song.timing.night <- lmer(minutes.til.dawn.sc ~ night_rain_scaled + (1|recorder) + (1|period), data = timing, REML = F)

song.timing.rain <- lmer(minutes.til.dawn.sc ~ rain_scaled + (1|recorder) + (1|period), data = timing, REML = F)

song.timing.temp <- lmer(minutes.til.dawn.sc ~ temp_scaled + (1|recorder) + (1|period), data = timing, REML = F)

song.timing.lunar <- lmer(minutes.til.dawn.sc ~ lunar_phase + (1|recorder) + (1|period), data = timing, REML = F)

song.timing.rain.night.temp <- lmer(minutes.til.dawn.sc ~ rain_scaled + night_rain_scaled + temp_scaled + (1|period) + (1|recorder), data = timing, REML = F)

song.timing.temp.rain <- lmer(minutes.til.dawn.sc ~ temp_scaled + rain_scaled + (1|recorder) + (1|period), data = timing, REML = F)

song.timing.lunar.temp.rain.night <- lmer(minutes.til.dawn.sc ~ lunar_phase + temp_scaled + rain_scaled + night_rain_scaled + (1|recorder) + (1|period), data = timing, REML = F)

song.timing.lunar.temp <- lmer(minutes.til.dawn.sc ~ lunar_phase + temp_scaled + (1|recorder) + (1|period), data = timing, REML = F)

song.timing.lunar.night <- lmer(minutes.til.dawn.sc ~ lunar_phase + night_rain_scaled + (1|recorder) + (1|period), data = timing, REML = F)

song.timing.night.temp <- lmer(minutes.til.dawn.sc ~ temp_scaled + night_rain_scaled + (1|recorder) + (1|period), data = timing, REML = F)

song.timing.temp_rain <- lmer(minutes.til.dawn.sc ~ temp_scaled * rain_scaled + (1|recorder) + (1|period), data = timing, REML = F)

song.timing.rain_night.temp <- lmer(minutes.til.dawn.sc ~ rain_scaled * night_rain_scaled + temp_scaled + (1|period) + (1|recorder), data = timing, REML = F)

song.timing.rain_scaled.night_temp <- lmer(minutes.til.dawn.sc ~ rain_scaled + night_rain_scaled * temp_scaled + (1|period) + (1|recorder), data = timing, REML = F)

song.timing.rain <- lmer(minutes.til.dawn.sc ~ rain_scaled + (1|recorder) + (1|period), data = timing, REML = F)

song.timing.lunar_temp.rain.night <- lmer(minutes.til.dawn.sc ~ lunar_phase * temp_scaled + rain_scaled + night_rain_scaled + (1|recorder) + (1|period), data = timing, REML = F)

song.timing.lunar.temp_rain.night <- lmer(minutes.til.dawn.sc ~ lunar_phase + temp_scaled * rain_scaled + night_rain_scaled + (1|recorder) + (1|period), data = timing, REML = F)

song.timing.lunar.temp.rain_night <- lmer(minutes.til.dawn.sc ~ lunar_phase + temp_scaled + rain_scaled * night_rain_scaled + (1|recorder) + (1|period), data = timing, REML = F)

song.timing.lunar.temp_rain_night <- lmer(minutes.til.dawn.sc ~ lunar_phase + temp_scaled * rain_scaled * night_rain_scaled + (1|recorder) + (1|period), data = timing, REML = F)

song.timing.lunar_temp_rain_night <- lmer(minutes.til.dawn.sc ~ lunar_phase * temp_scaled * rain_scaled * night_rain_scaled + (1|recorder) + (1|period), data = timing, REML = F)

song.timing.lunar_temp.rain.night <- lmer(minutes.til.dawn.sc ~ lunar_phase * temp_scaled + rain_scaled + night_rain_scaled + (1|recorder) + (1|period), data = timing, REML = F)

song.timing.lunar_temp_rain.night <- lmer(minutes.til.dawn.sc ~ lunar_phase * temp_scaled * rain_scaled + night_rain_scaled + (1|recorder) + (1|period), data = timing, REML = F)

song.timing.lunar_temp <- lmer(minutes.til.dawn.sc ~ lunar_phase * temp_scaled + (1|recorder) + (1|period), data = timing, REML = F)

song.timing.lunar_rain <- lmer(minutes.til.dawn.sc ~ lunar_phase * rain_scaled  + (1|recorder) + (1|period), data = timing, REML = F)

song.timing.lunar.rain <- lmer(minutes.til.dawn.sc ~ lunar_phase + rain_scaled  + (1|recorder) + (1|period), data = timing, REML = F)

song.timing.lunar_night <- lmer(minutes.til.dawn.sc ~ lunar_phase * night_rain_scaled  + (1|recorder) + (1|period), data = timing, REML = F)

song.timing.night_temp <- lmer(minutes.til.dawn.sc ~ temp_scaled * night_rain_scaled + (1|recorder) + (1|period), data = timing, REML = F)

song.timing.rain_night <- lmer(minutes.til.dawn.sc ~ rain_scaled * night_rain_scaled + (1|recorder) + (1|period), data = timing, REML = F)

song.timing.night_temp <- lmer(minutes.til.dawn.sc ~ night_rain_scaled * temp_scaled + (1|recorder) + (1|period), data = timing, REML = F)

song.timing.temp_night <- lmer(minutes.til.dawn.sc ~ temp_scaled * night_rain_scaled + (1|recorder) + (1|period), data = timing, REML = F)

# AIC Comparison
AICtab(song.timing.intercept,song.timing.night, song.timing.rain, song.timing.temp, song.timing.lunar, song.timing.rain.night.temp, song.timing.night.temp, song.timing.temp.rain, song.timing.lunar.temp.rain.night, song.timing.lunar.temp, song.timing.lunar.rain, song.timing.lunar.night, song.timing.night_temp, song.timing.rain_night.temp, song.timing.lunar_temp.rain.night, song.timing.lunar.temp_rain.night, song.timing.lunar.temp.rain_night, song.timing.lunar.temp_rain_night, song.timing.lunar_temp_rain_night, song.timing.lunar_temp, song.timing.lunar_rain, song.timing.lunar_night, song.timing.rain_night,song.timing.temp_rain, weights=T, base=T)

# Model Summaries
summary(song.timing.temp.rain)
summary(song.timing.temp_rain)
```


```{R}

# Create a dataset with the data centred in the morning (before 14)
timing_morning <- timing %>% filter(minutes.til.dawn < 581.7)

# Scale variables
timing_morning$rain_scaled <- scale(timing_morning$rain)
timing_morning$temp_scaled <- scale(timing_morning$temp)
timing_morning$night_rain_scaled <- scale(timing_morning$night_rain)
timing_morning$minutes.til.dawn.sc <- scale(timing_morning$minutes.til.dawn)

# Models
song.timing.intercept <- lmer(minutes.til.dawn.sc ~ (1|recorder) +(1|period), data = timing_morning, REML = F)

song.timing.night <- lmer(minutes.til.dawn.sc ~ night_rain_scaled  + (1|recorder) +(1|period), data = timing_morning, REML = F)

song.timing.rain <- lmer(minutes.til.dawn.sc ~ rain_scaled + (1|recorder)+(1|period) , data = timing_morning, REML = F)

song.timing.temp <- lmer(minutes.til.dawn.sc ~ temp_scaled +(1|recorder) + (1|period), data = timing_morning, REML = F)

song.timing.lunar <- lmer(minutes.til.dawn.sc ~ lunar_phase + (1|recorder)+(1|period), data = timing_morning, REML = F)

song.timing.rain.night.temp <- lmer(minutes.til.dawn.sc ~ rain_scaled + night_rain_scaled + temp_scaled +(1|period) +(1|recorder), data = timing_morning, REML = F)

song.timing.temp.rain <- lmer(minutes.til.dawn.sc ~ temp_scaled + rain_scaled + (1|recorder)+(1|period), data = timing_morning, REML = F)

song.timing.lunar.temp.rain.night <- lmer(minutes.til.dawn.sc ~ lunar_phase + temp_scaled + rain_scaled + night_rain_scaled + (1|recorder)+(1|period), data = timing_morning, REML = F)

song.timing.lunar.temp <- lmer(minutes.til.dawn.sc ~ lunar_phase + temp_scaled + (1|recorder)+(1|period), data = timing_morning, REML = F)

song.timing.lunar.rain <- lmer(minutes.til.dawn.sc ~ lunar_phase * rain_scaled  + (1|recorder)+(1|period), data = timing_morning, REML = F)

song.timing.lunar.night <- lmer(minutes.til.dawn.sc ~ lunar_phase  + night_rain_scaled  + (1|recorder)+(1|period), data = timing_morning, REML = F)

song.timing.night.temp <- lmer(minutes.til.dawn.sc ~ temp_scaled + night_rain_scaled +(1|recorder) + (1|period), data = timing_morning, REML = F)

song.timing.temp_rain <- lmer(minutes.til.dawn.sc ~ temp_scaled * rain_scaled + (1|recorder)+(1|period), data = timing_morning, REML = F)

song.timing.rain_night.temp <- lmer(minutes.til.dawn.sc ~ rain_scaled * night_rain_scaled + temp_scaled +(1|period) +(1|recorder), data = timing_morning, REML = F)

song.timing.rain.night_temp <- lmer(minutes.til.dawn.sc ~ rain_scaled + night_rain_scaled * temp_scaled +(1|period) +(1|recorder), data = timing_morning, REML = F)

song.timing.rain <- lmer(minutes.til.dawn.sc ~ rain_scaled + (1|recorder)+(1|period), data = timing_morning, REML = F)

song.timing.lunar_temp.rain.night <- lmer(minutes.til.dawn.sc ~ lunar_phase * temp_scaled + rain_scaled + night_rain_scaled + (1|recorder)+(1|period), data = timing_morning, REML = F)

song.timing.lunar.temp_rain.night <- lmer(minutes.til.dawn.sc ~ lunar_phase + temp_scaled * rain_scaled + night_rain_scaled + (1|recorder)+(1|period), data = timing_morning, REML = F)

song.timing.lunar.temp.rain_night <- lmer(minutes.til.dawn.sc ~ lunar_phase + temp_scaled + rain_scaled * night_rain_scaled + (1|recorder)+(1|period), data = timing_morning, REML = F)

song.timing.lunar.temp_rain_night <- lmer(minutes.til.dawn.sc ~ lunar_phase + temp_scaled * rain_scaled * night_rain_scaled + (1|recorder)+(1|period), data = timing_morning, REML = F)

song.timing.lunar_temp_rain_night <- lmer(minutes.til.dawn.sc ~ lunar_phase * temp_scaled * rain_scaled * night_rain_scaled + (1|recorder)+(1|period), data = timing_morning, REML = F)

song.timing.lunar_temp.rain.night <- lmer(minutes.til.dawn.sc ~ lunar_phase * temp_scaled + rain_scaled + night_rain_scaled + (1|recorder)+(1|period), data = timing_morning, REML = F)

song.timing.lunar_temp_rain.night <- lmer(minutes.til.dawn.sc ~ lunar_phase * temp_scaled * rain_scaled + night_rain_scaled + (1|recorder)+(1|period), data = timing_morning, REML = F)

song.timing.lunar_temp <- lmer(minutes.til.dawn.sc ~ lunar_phase * temp_scaled + (1|recorder)+(1|period), data = timing_morning, REML = F)

song.timing.lunar_rain <- lmer(minutes.til.dawn.sc ~ lunar_phase * rain_scaled  + (1|recorder)+(1|period), data = timing_morning, REML = F)

song.timing.lunar_night <- lmer(minutes.til.dawn.sc ~ lunar_phase * night_rain_scaled  + (1|recorder)+(1|period), data = timing_morning, REML = F)

song.timing.night_temp <- lmer(minutes.til.dawn.sc ~ temp_scaled * night_rain_scaled +(1|recorder) + (1|period), data = timing_morning, REML = F)

song.timing.rain_night <- lmer(minutes.til.dawn.sc ~ rain_scaled * night_rain_scaled + (1|recorder) + (1|period), data = timing_morning, REML = F)

song.timing.night_temp <- lmer(minutes.til.dawn.sc ~ night_rain_scaled * temp_scaled + (1|recorder) + (1|period), data = timing_morning, REML = F)

song.timing.rain.lunar.temp <- lmer(minutes.til.dawn.sc ~ night_rain_scaled + lunar_phase + temp_scaled + (1|recorder) + (1|period), data = timing_morning, REML = F)

# AIC comparison
AICtab(song.timing.intercept, song.timing.night, song.timing.rain, song.timing.temp, song.timing.lunar,song.timing.rain.night.temp, song.timing.temp.rain, song.timing.lunar.temp.rain.night, song.timing.lunar.temp,song.timing.lunar.rain, song.timing.lunar.night, song.timing.night_temp, song.timing.rain_night.temp, song.timing.rain.night_temp, song.timing.lunar_temp.rain.night, song.timing.lunar.temp_rain.night, song.timing.lunar.temp.rain_night, song.timing.lunar.temp_rain_night, song.timing.lunar_temp_rain_night, song.timing.lunar_temp, song.timing.lunar_rain, song.timing.lunar_night, song.timing.rain.lunar.temp, song.timing.rain_night, song.timing.temp_rain, weights=T, base=T)

# Model Summaries
summary(song.timing.rain)

# VIF Check
VIF <- prova_timing
predictor_vars <- c("temp_night", "temp_day", "night_rain")
lm_model <- lm(minutes.til.dawn ~ ., data = VIF[, c("minutes.til.dawn", predictor_vars)])
car::vif(lm_model)

```
